Transition from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-11-16 manuscript/manuscript.Rmd
Fix dates in the results.

The transition calculations shows that between 1985 and 2021, 64874 squared kilometers of forests were converted to agriculture, in the Brazilian Amazon biome.
The length of the transitions can go from 1 to 36 years, in which transitions closer to 1 year are considered as fast transitions, and transitions closer to 36 years are considered as slow transitions.
Transitions of 1 year are considered as "direct" transitions, where there were no presence of pasture before the establishment of agriculture, out estimations shows that around 9.2 % of the transitions are considered as "direct".

Although we named as deforestation the last years identified as forest before classification of anthropic cover, we acknowledge that it is not a direct measurement of deforestation (such as PRODES), it is however a proxy to deforestation.

>>>>

The transition calculations shows that between 1985 and 2021, 64874 squared kilometers of forests were converted to agriculture, in the Brazilian Amazon biome.
The length of the transitions can go from 0 to 35 years, in which transitions closer to 0 year are considered as fast transitions, and transitions closer to 35 years are considered as slow transitions.
Transitions of 0 year are considered as "direct" transitions, where there were no presence of pasture before the establishment of agriculture, our estimations shows that around 9.2 % of the transitions are considered as "direct".

Although we named as deforestation the last years identified as forest before classification of antropic cover, we acknowledge that it is not a direct measurement of deforestation (such as PRODES), it is however a proxy to deforestation.

### 2022-11-16 manuscript/manuscript.tex
Fix dates in the results.

The transition calculations shows that between 1985 and 2021, 64874 squared kilometers of forests were converted to agriculture, in the Brazilian Amazon biome.
The length of the transitions can go from 1 to 36 years, in which transitions closer to 1 year are considered as fast transitions, and transitions closer to 36 years are considered as slow transitions.
Transitions of 1 year are considered as ``direct'' transitions, where there were no presence of pasture before the establishment of agriculture, out estimations shows that around 9.2 \% of the transitions are considered as ``direct''.

Although we named as deforestation the last years identified as forest before classification of anthropic cover, we acknowledge that it is not a direct measurement of deforestation (such as PRODES), it is however a proxy to deforestation.

>>>>

The transition calculations shows that between 1985 and 2021, 64874 squared kilometers of forests were converted to agriculture, in the Brazilian Amazon biome.
The length of the transitions can go from 0 to 35 years, in which transitions closer to 0 year are considered as fast transitions, and transitions closer to 35 years are considered as slow transitions.
Transitions of 0 year are considered as ``direct'' transitions, where there were no presence of pasture before the establishment of agriculture, our estimations shows that around 9.2 \% of the transitions are considered as ``direct''.

Although we named as deforestation the last years identified as forest before classification of antropic cover, we acknowledge that it is not a direct measurement of deforestation (such as PRODES), it is however a proxy to deforestation.
